---
title: "Modeling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
```


# Import data

```{r}
df = read.csv("bank-additional-full 2 (4) (2).csv", sep = ';')

```




## Data Cleaning for sanity checking



```{r}
df = df[df$age>=18,]
mask = (df$poutcome == 'nonexistent') != (df$pdays==999)
df['pdays'][mask,] = 10

```


## Data preprocessing for logistic regression 

### subsetting: 

exclude `duration`
```{r}
df = df[, 1:15]
df = df[, -11]
df
```


### bucketing
```{r}
# bucket pdays into categories: "contacted" and "not contacted"
df = mutate(df, pdays_bucket=case_when(
  df$pdays ==999 ~ 'not contacted',
  df$pdays !=999 ~ 'contacted'
))
df
```


```{r}
print(table(df$pdays_bucket)/length((df$pdays_bucket)))
print(table(df$poutcome)/length((df$pdays)))
print(table(df$previous)/length((df$pdays)))
```

Here, since `pdays`, `previous` and `poutcome` are highly correlated, since 86% of customers were not previously contacted. So I would choose one of the feature for the model. 
**I decide to go with `poutcome`**

### create dummy variables for `job`

```{r}
str(df)
sum(df$education=='illiterate')
```


```{r}
library(fastDummies)
```

```{r}
df = dummy_cols(.data = df, select_columns = c('job'), remove_first_dummy = TRUE, remove_selected_columns = T)
```



### One thing to think about `education`

Should I transform `education` to a numerical? In a social science perspective it is well acceptable, which is also indicated in the naming of the categories. 

** this remains questionable, so I'll leave this variable out for the initial trial for analysis** 




```{r}

#create a new variable   `education_num` that is numeric
df = mutate(df, education_num = case_when(df$education=='illiterate'~0,
                                         df$education=='basic.4y'~4,
                                         df$education=='basic.6y'~6,
                                         df$education=='basic.9y'~9,
                                         df$education=='high.school'~12,
                                         df$education=='professional.course'~14,
                                         df$education=='university.degree'~16,
                                         df$education=='unknown'~NaN))
```


```{r}

```





